Analysis of celiac disease

### 2018-03-14 5-results-celiac.Rmd
change colors

bigstatsr:::MY_THEME(
  ggplot(scores_tidy, aes(d = d, m = Score, color = Method, linetype = Method)) +
    style_roc(xlab = "1 - Specificity", ylab = "Sensitivity")
) +
  geom_roc(n.cuts = 0, size = 2) +
  theme(legend.position = c(0.7, 0.3), legend.key.width = unit(4, "line")) +
  coord_equal()
```

>>>>

methods.color <- setNames(scales::hue_pal()(6), 
                          c("logit-simple", "PRS-max", "PRS-stringent",
                            "T-Trees", "logit-triple", "PRS-all"))

bigstatsr:::MY_THEME(
  ggplot(scores_tidy, aes(d = d, m = Score, color = Method, linetype = Method)) +
    style_roc(xlab = "1 - Specificity", ylab = "Sensitivity")
) +
  geom_roc(n.cuts = 0, size = 2) +
  theme(legend.position = c(0.7, 0.3), legend.key.width = unit(4, "line")) +
  coord_equal() +
  scale_color_manual(values = methods.color)
```
